\subsection{Coarse Particulate Matter Density}

To estimate the density of the CPOM in small ponds in central Virgina we used an Ekman dredge to collect sediment samples from the littoral and open water regions of Daulton Pond, Lancer Park Pond, Woodland Court Pond, and Wilkes Lake. We collected 2 replicate samples from 3 haphazardly chosen locations in the littoral zone and open water portions for Daulton Pond, Woodland Court Pond, and Wilkes Lake on 13 May 2013, 14 May 2013, and 14 June 2013 respectively. We collected 3 replicate samples each from a single littoral and a single open water location in Lancer Park Pond on 20 March 2013.  Finaly we collected a single sample from 3 littoral locations and 6 open water locations in Wilkes Lake on 20 Febuary 2013. In all cases littoral samples were collected between approximately 5 and 20 m from the shoreline be the actual distance was not recorded.  The open water samples were collected variable distances from the shoreline but all relatively close to the center of the ponds.

All Ekman samples were sieved through a 250 $\mu m$ mesh. The material retained by the sieve was preserved in 70\% (v:v) ethanol and transported back to the lab.  In the lab the preserved material was passed through a 1 mm sieve and all retained material was dried at 50 \textsuperscript{o}C for 48 h.  The dried material was then homogenized with a mortar and pestal and a subsample was ashed at 550 \textsuperscript{o}C for 4 h to determine the proportion of organic matter in the sample via loss on ignition (LOI).  The dry mass was multiplied by the proportion of organic matter in the sample to calculate the ash--free--dry--mass (AFDM).
  
  