\subsection{Leaf Litter Decomposition}

To determine the leaf litter decomposition rate in the ponds, we incubated tulip poplar leaves that had been collected by gently pulling senescent leaves from the tree. Only leaves that released without resistance were used.  The leaves were all collected and air--dried during the fall of 2013.  The leaf packs were assembled by placing 5.0 g of intact, dried tulip poplar leaved into plastic produce bags with approximately 9 mm\textsuperscript{2} mesh. The bags were sealed and attached to a float and a small bag of rocks as an anchor.  The bags were placed into the littoral zone of Campus Pond and Daulton Pond on 22 October 2013 and into the littoral zone of Lancer Park Pond on 29 October 2013. To determine the mass lost due to handling and deployment, 5 bags were immediately harvested following deployment. Bags were harvested by gently moving the bag into a 250 $\mu$ m mesh net underwater gently removing from the lake. The bag and any macroinvertebrates retained in the net were then placed into a VOLUME zip-loc bag and returned to the lab.  The remaining leaf material was gently rinsed over a 1 mm mesh sieve to remove all macroinvertebrates and then placed into a pre--weighed paper bag and dried at 50\textsuperscript{o} C for at least 48 h.  The dried leaf material was then weighed and homogenized with a mortar and pestle. This homogenized material was then ashed at 550\textsuperscript{o} C to determine the AFDM of the leaves. The dates that the remaining leaves were harvested from each pond is shown in Table \ref{tab:ponds}. 