%NutrientFlux

\subsection{Nutrient Flux}

The lake water added to the experiment initially (10 June 2014), had 0.034, 0.084, and 0.008 mg L\textsuperscript{-1} of NO\textsubscript{2}--N + NO\textsubscript{3}--N, NH\textsubscript{4}--N, and ortho-phosphate, respectively. The bottles enriched with DIN and DIP had 0.184, 0.195, and 0.012 mg L\textsuperscript{-1} NO\textsubscript{2}--N + NO\textsubscript{3}--N, NH\textsubscript{4}--N, and ortho-phosphate, respectively.

Overall the change in DIN and DIP concentrations in the bottles was low and the different nutrients varied in how they were affected by the duration of incubation and the presence of leaf litter or added nutrients (Fig. \ref{fig:nut_flux}).  The nitrate + nitrite flux was significantly affected by the presence of leaf litter and the day of the incubation (Table \ref{tab:nut_anova}). However, there was a significant interaction between leaf litter and incubation day, indicating that the effect of leaf litter was not consistent across all of the incubation days (Table \ref{tab:nut_anova}, Fig. \ref{fig:nut_flux}). On the second day of the incubation the bottles without leaf litter showed an increase in nitrate + nitrite that ranged 37.5 and 181.1 mg N m\textsuperscript{-2} d\textsuperscript{-1}, while the bottles with leaf litter showed essentially no net change with a range of -2.4 to 2.9 mg N m\textsuperscript{-2} d\textsuperscript{-1} (Fig. \ref{fig:nut_flux}).  A difference in the change in nitrate + nitrite between the bottles with and without leaf litter was also evident on day 7 but the bottles with leaf litter showed a greater increase in nitrate + nitrite (Fig. \ref{fig:nut_flux}). The change in nitrate + nitrite on day 7 ranged -41.0 to 3.6 mg N m\textsuperscript{-2} d\textsuperscript{-1} and -20.4 to 37.2 mg N m\textsuperscript{-2} d\textsuperscript{-1} in the bottles lacking and containing leaf litter, respectively. 

The change in the ammonium concentration ranged from -4.6 to 7.4 mg N m\textsubscript{-2} d\textsubscript{-1} with a mean change of -0.69 mg N m\textsuperscript{-2} d\textsuperscript{-1} and was not affected by the days of incubation, or the presence of leaf litter or added nutrients (Table \ref{tab:nut_anova}, Fig. \ref{fig:nit_flux}).

The change in ortho--phosphate concentration was significantly affected by the days of incubation (Table \ref{tab:nut_anova}). On days 2 and 7 of the incubation there was an increase in the ortho--phosphate concentration followed by a decline in the change in concentration as the incubation progressed (Fig. \ref{fig:nut_flux}). There was no effect of the leaf litter or added nutrients on the change in ortho--phosphate concentration (Table \ref{tab:nut_anova}).

