\subsection{Statistical Analysis}

Differences in CPOM density among ponds and between the littoral and open water zones of all ponds was determined using ANOVA. The leaf litter density was natural log transformed to homogenize the variance in the test of pond differences and for the test between the littoral and open water samples. Specific differences among ponds were assessed with a Tukey HSD post-hoc test. The relationship between CPOM density and the percent organic matter of the sediments was assessed using linear regression.

The decay coefficent for the leaves in the litter bags in each pond were determined by calculating the slope of the relationship between the natural log of the percent leaf mass remaining by the number of days in the pond.

In the litter experiment and leached litter experiment differences in the mass loss of the leaves in the different treatment levels over the course of the experiment was tested using ANOVA. Changes in the percent C and percent N of the leaves in the different treatment levels of the litter and leached litter experiments was assessed with Kruskal Wallace rank sum tests, however the changes in leaf C and N mass among treatments in the leached litter experiment were assesses with ANOVA. In the litter experiment, the difference between the area-normalized ergosterol mass of the leaves and the surface sediments was tested with a Kruskal Wallace rank sum test.

The effect of days of incubation, and treatment levels on SOD, dissolved oxygen concentration in the overlying water,  and S\textsubscript{R} in the litter and leached litter SOD experiments, as well as, nutrient flux in the litter experiment was assessed with a linear mixed models using the lme4 package \cite{lme4} in R. Treatment differences were evaluated with type III sums of squares and Satterthwaite approximation for degrees of freedom.

All statistical analysis was performed using R \cite{R}

